### 2019-07-22 .archive/Documents/literature_review/backup/review_content.backup.tex
Changes; - Added inital files for Thesis write up - Ordered and restructured various documents - Moved old lit' review into the .archive

% \section{Possible research questions}

% Overall the research will aim to investigate the strength of pEp's Trustword fingerprint mappings, and the ease in which partial collisions can be obtained for keys and how this will ultimately affect the end user(s).

% Key areas that will be looked into:
% \begin{itemize}
%     \item Is the recommended minimum number of Trustwords enough to provide a basic level of security.
%     \item What attributes make a strong general wordlist for fingerprint mapping and does the Trustword implementation exhibit these features.
%     \item How easy is it to generate similar keys that attack a targeted key pair?
%     \item How can similarity be quantified in terms of words? Does this include pronunciation or visual aspects?
%     \item As usability is the main justification for the use of Trustwords are there alternatives that provide the same usability but with more security?
% \end{itemize}

\section{Review - Fingerprint representations}

@@

Current research in ways to represent and validate fingerprints has almost exclusively focused on the usability of such schemes. The following section will individually discuss available research findings alongside an overall comparison of the research recommendations.

\textbf{Hsu-Chun Hsiao, \textit{et. al.}} produced the first work in this area in their paper: \textit{A Study of User-Friendly Hash Comparison Schemes}\cite{hsiao2009study} in around 2009. The aim of the study was to provide the first insight into the best encoding scheme used to represent a hash fingerprint. The schemes used were Base32, English words, Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Flag Ext\footnote{The author's own improvement on Flag} and finally Chinese, Korean and Japanese symbol encoding. A total of 436 participants were assessed in the study.

Alongside the main aim of the paper, the authors wanted to provide empirical links between participant attributes (such as age or gender) and performance with the encoding scheme. This is something rarely seen in the related research. Hsu-Chun Hsiao \textit{et al.} also provided two categories of similarities; ``hard'' and ``easy''. These were designed to be the worst and best case respectively. As a final aim and the reason for the inclusion of Chinese, Korean and Japanese characters was to research if being a native speaker assists the user in distinguishing subtle differences between encodings in the respective language. The entropy of encodings ranged from 22-bits to 28-bits. This is extremely low in comparison to similar research. However, this can be attributed to the age of the paper. \\
The authors' decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes) was due to their similarity to Base32 and their well-known deficiencies. This is not consistent with available research. For example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}\cite{dechand2016empirical} it was shown numerical representations performed significantly better than that of Base32.

@@

In conclusion, the paper provided a very strong foundation for further research due to the wide variety of topics touched upon. However, its age means that results cannot be applicable to modern day scenarios, and oversights in the development of the study such as the exclusion of hexadecimal encoding and the lack of information gained on the perceived usability of the scheme from users results in an ultimately incomplete study.

\textbf{Kainda \textit{et al.}}\cite{kainda2009usability} in 2009 investigated fingerprint representations and comparison methods in the context of using humans as the Out-Of-Band (OOB) channel for secure device pairing. This study was comprehensive and assessed a wide variety of concepts. This is one of the few papers in the literature that assessed the way to compare encodings alongside the representations themselves. For comparison methods the paper looked into ``Compare-and-Confirm'', ``Compare-and-Select'', ``Compare-and-Enter'' and ``Barcode'' scanning. This set includes the most common ways of comparison according to available research. Alongside this, the paper reviews Numerical, Alphanumerical, Words, Sentences, Images, Melodies and Sound (Numerical/Alphanumerical). Again, this in comparison to similar literature is highly comprehensive.

In terms of empirical data gathered by the paper, they reviewed the time completed to asses the representation and the number of security and non-security related errors. Furthermore, the authors also collected user opinion on ease-of-use, satisfaction and confidence of the reviewed schemes. The overall schemes were then quantified using a metric known as the Single Usability Metric (SUM)\cite{sauro2005method}. This provides an elementary way to rank and compare the schemes, thus improving the usability of the results. 
However, the one apparent downside to the experimental side of the study is the 40 participants enrolled. This is one of the smallest sizes of enrolment in the literature and thus, puts a possible limit on the accuracy and applicability of the obtained results.

Overall, if usability is the only consideration the paper ranked the comparison methods: Compare-and-Confirm, Compare-and-Enter, Compare-and-Select and Barcode. If, however, the consideration of security alongside usability is required the best is: Compare-and-Enter, Barcode, Compare-and-Confirm and Compare-and-Select. Research has been limited in this area of modes of comparison, however, the results from this paper are consistent with the limited alternative literature. In terms of encoding schemes, the paper ranked Numerical, Alphanumerical and Words as the top three encoding schemes (These were all with Compare-and-Confirm). This took into consideration the usability and security of the scheme. This is relatively consistent with other literature where numerical and written encoding schemes seem to be the most effective overall.

In conclusion, this paper provided a highly comprehensive review of all the aspects of human fingerprint verification, where it reviewed all the elements involved in the process. The only limitation of the paper is the size of the participants enrolled for the study.

\textbf{Ersin Uzun \textit{et al.}}\cite{uzun2007usability} exclusively reviewed comparison methods. This is performed in the context of ``Secure device pairing'' and thus some comparison schemes are tested that are not relevant in a fingerprint comparison context, for example  ``Choose-and-Enter'' (A participant chooses a passphrase from an available list and enters it into the other device). Thus, only relevant comparison scheme and their results have been extracted and compared.

The relevant comparison methods tested were,Compare-and-Confirm, Compare-and-Select and Compare-and-Enter. These are almost exactly the same encoding schemes assessed in the relevant research literature. The paper also had two rounds of experiments including 40 participants each where changes were made to UX and format between these studies. 
Due to the ``Secure device pairing'' context, consideration needs to be made into the actual strings being encoded. Due to secure device pairing commonly utilising Short Authentication Strings (SAS) the
paper only reviewed encodings of 4 digit long strings. This, therefore,limits the applicability of the results in comparison to other fingerprint encoding literature. Between the two rounds, the authors dropped ``Confirm-and-Enter'' due to its low usability and over similarity to a similar scheme called ``Copy'' (used for passphrase verification). The low rating for Confirm-and-Enter is in contrast with research performed by Kainda \textit{et al.}\cite{kainda2009usability} They ranked Confirm-and-Enter as the 2nd most usable system. With changes to the UX of Confirm-and-Confirm backed up by external research \cite{palmer1990attentional}\cite{hammer2009category} the second round of research was performed with a new set of participants. The alterations took Compare-and-Confirm from 20\% to 0\% fatal error rate (FER). The same trend for Confirm-and-Select with it reducing its FER from 12.5\% to 5\%. The authors, therefore, recommended ``Compare-and-Confirm'' as the overall best choice for comparison methods. Again, comparing this word to the most similar work done by Kainda \textit{et al.}\cite{kainda2009usability} this is consistent with their findings where they ranked ``Compare-and-Confirm'' as the most secure comparison method.

Overall, the paper provides a sizeable insight into suitable methods of comparison, this is due to the cross over between fingerprint comparison and secure device pairing. This paper is limited in terms of the short strings compared, the different overall research aim and the size of the number of participants used in the studies. In terms of security of the schemes, the results were consistent with that of alternative research but clashed when usability was considered. This, however, may be due to the differing use-cases of the comparison methods.

@@

In conclusion for this section, there has been extensive work in the investigation of the usability of textual and visual encoding schemes alongside methods of comparison. There are mixed opinions about visual representations, however, the majority defines them as easy to use but severely lacking in security. Research on textual representations, however, is in agreement; natural language based encodings such as words or sentences provide some of the highest usability and security over the baseline performance of alphanumerical encodings. The literature also concurs on the use of Compare-and-Confirm as the best method of comparing fingerprints overall, with Compare-and-Select being highlighted for its poor security and usability.\\
The starkest limitations of the literature are the range of participant and encoding entropy, where at its worst only 22-bits of entropy were tested. Another limitation is the scant amount of research solely investigating modes of comparison, where the literature only contains two papers with this aim. Even these limitations, as a whole the literature on this topic has provided a relatively comprehensive and coherent view on the usability of textual and visual hash encoding schemes.

>>>>

\section{Introduction}
The increasing use of public key cryptography by instant messaging and secure email means key fingerprint 
verification is an ever more important task. One of the biggest risks to the security of the communication channel is a Man-in-the-middle (MiTM) attack . A successful MiTH attack can circumvent the encryption as it allows an attacker to read all the encrypted data. A countermeasure for this is the verification of each parties' fingerprint. \textbf{[...]}

\textbf{TODO: } Finish introduction

\section{Literature Review}

@@

\textbf{TODO: } - Improve the flow of the first section, need to phrase it like I'm telling a story
\textbf{TODO: } - Create written introduction setting the scene. \\
\textbf{TODO: } - Add participant size to M. Shirvanian (25) \\
\textbf{TODO: } - Create a background section for Compare-and-X
\\
\textbf{TODO: } - Create comparison area where inconsistencies are compared

% \textbf{TODO: } - Check evaluation with each paper in regards to:
% \begin{itemize}
%     \item Participant size [P]
%     \item Social aspects, where have they come from? Age? Gender? Occupation?  [S]
%     \item Target entropy [E]
%     \item Attacker strength [A]
% \end{itemize}
% [P, S, E, A]

Current research into human-based validation of fingerprints has almost exclusively focused on the usability of such schemes. The following section will individually discuss available research findings alongside an overall comparison of the research recommendations.

% [A]
Some of the first work in this area was performed by \textbf{Hsu-Chun Hsiao, \textit{et al.}}\cite{hsiao2009study}. The main aim of the study was to provide the first insight into the best encoding schemes used to represent a hash fingerprint. The schemes used were Base32, English words, Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Flag Ext\footnote{The authors' own improvement on Flag} and finally Chinese, Korean and Japanese symbolic encodings. A total of 436 participants were assessed in the study.

In addition to the central aims of the paper, the authors intended to provide empirical links between participant attributes (such as age or gender) and performance with the encoding scheme. This is something rarely seen in the related research. Hsu-Chun Hsiao \textit{et al.} also provided two categories of similarities; ``hard'' and ``easy''. ``Hard'' pair only have a very small difference, therefore, difficult to distinguish. These were designed to be the worst and best case respectively. The reasoning behind inclusion of Chinese, Korean and Japanese characters was to investigate the links between language ability and distinguishing subtle differences between encodings in the respective language. The entropy of encodings ranged from 22-bits to 28-bits. This is the lowest level of entropy used in the assessed literature. To quantify this a hash rate of 10 MH/s SHA-1 compressions would be able to find a match for 28-bits in 26.8 seconds. This is addressed by the author at a stage in the paper where they state \textit{``However, increasing entropy is not a solution because it sacrifices usability and accuracy. With more entropy, representations will contain longer sequences of characters or more minute details which will lead to increased time and errors during comparisons.''}. This claim is entirely unsubstantiated with any empirical evidence alongside no discussion into why the level of entropy was chosen. This, however, was followed by in interesting recommendation into the use of commitments\cite{blum1982coin}. This provides an attacker with a single chance to find a collision, thus, providing a valid use case for low levels of entropy.\\
Another limitation is the authors' decision to exclude hexadecimal and numerical encodings (some of the most widespread encoding schemes). This was based on their own claims on similarities to Base32 and ``well-known deficiencies" in the excluded schemes. This point was provided with no further justification or quantified in any way. It is also not consistent with available research, for example, in \textit{``Empirical Study of Textual Key-Fingerprint Representations''}\cite{dechand2016empirical} it was shown numerical representations performed significantly better than that of Base32.

@@

In conclusion, the paper touched upon a wide variety of topics. Moreover, the consideration into the attributes of participants and consideration into how this would affect their performance with the scheme was a substantial addition. This provides a higher level of validity to the results and is something severely lacking from the literature assessed. However, the age of the study limits the applicability to modern day scenarios, and oversights in the development of the study such as the exclusion of hexadecimal encoding and the lack of information gained on the perceived usability of the scheme from users results in an incomplete study. In addition, the paper failed to consider the quantification of attacker strength and, therefore, failed to discuss the feasibility of these attacks.

% [A]
\textbf{Kainda \textit{et al.}}\cite{kainda2009usability} in 2009 investigated fingerprint representations and comparison methods in the context of using humans as the Out-Of-Band (OOB) channel for secure device pairing. This study was comprehensive and assessed a wide variety of concepts. This is one of the few papers in the literature that assessed the way to compare encodings alongside the representations themselves. For comparison methods the paper looked into ``Compare-and-Confirm'', ``Compare-and-Select'', ``Compare-and-Enter'' and ``Barcode'' scanning. This set includes the most common ways of comparison according to available research. Alongside this, the paper reviews Numerical, Alphanumerical, Words, Sentences, Images, Melodies and Sound (Numerical/Alphanumerical). Again, this in comparison to similar literature is highly comprehensive.

In terms of empirical data gathered by the paper, they reviewed the time completed to asses the representation and the number of security and non-security related errors. Furthermore, the authors also collected user opinion on ease-of-use, satisfaction and confidence of the reviewed schemes. The overall schemes were then quantified using a metric known as the Single Usability Metric (SUM)\cite{sauro2005method}. This provides an elementary way to rank and compare the schemes, thus improving the potential validity of the results. 
However, the one apparent downside to the experimental side of the study is the 30 participants enrolled. This is one of the smallest sizes of enrolment in the literature and thus, puts a possible limit on the reliability and applicability of the obtained results. This limitation was, however,  supplemented by a consideration into the demographics of the participants enrolled. The participants were evenly split between male and female alongside an age range of 18 to 75.

Overall, if usability is the only consideration the paper ranked the comparison methods: Compare-and-Confirm, Compare-and-Enter, Compare-and-Select and Barcode. If, however, the consideration of security alongside usability is required the best is: Compare-and-Enter, Barcode, Compare-and-Confirm and Compare-and-Select. Research has been limited in this area of modes of comparison, however, the results from this paper are consistent with the limited alternative literature. In terms of encoding schemes, the paper ranked Numerical, Alphanumerical and Words as the top three encoding schemes (These were all with Compare-and-Confirm). This recommendation took into consideration the usability and security of the scheme and is relatively consistent with other research where numerical and English language based encoding schemes seem to be the most effective overall.

In conclusion, this paper provided a highly comprehensive review of all the aspects of human fingerprint verification, where it reviewed all the elements involved in the process. Limitations of the paper involved the inconsistent and low range of entropy (20-bits to 40-bits)alongside the size of the participants enrolled for the study.

% TODO: Implement checks below:
\textbf{Ersin Uzun \textit{et al.}}\cite{uzun2007usability} exclusively reviewed comparison methods. This is performed in the context of ``Secure device pairing'' and thus some comparison schemes are tested that are not relevant in a fingerprint comparison context, for example  ``Choose-and-Enter'' (A participant chooses a passphrase from an available list and enters it into the other device). Thus, only relevant comparison scheme and their results have been extracted and compared.

The relevant comparison methods tested were, 
``Compare-and-Confirm'', ``Compare-and-Select'' and ``Compare-and-Enter''. These are almost exactly the same encoding schemes assessed in the relevant research literature. The paper also had two rounds of experiments including 40 participants each where changes were made to UX and format between these studies. 
Due to the ``Secure device pairing'' context, consideration needs to be made into the actual strings being encoded. Due to secure device pairing commonly utilising Short Authentication Strings (SAS) the
paper only reviewed encodings of 4 digit long strings. This, therefore, limits the applicability of the results in comparison to other fingerprint encoding literature. Between the two rounds, the authors dropped Confirm-and-Enter due to its low usability and over similarity to a similar scheme called ``Copy'' (used for passphrase verification). The low rating for Confirm-and-Enter is in contrast with research performed by Kainda \textit{et al.}\cite{kainda2009usability} where they ranked Confirm-and-Enter as best method overall. With changes to the UX of Compare-and-Confirm backed up by external research \cite{palmer1990attentional}\cite{hammer2009category} the second round of research was performed with a new set of participants. The alterations took Compare-and-Confirm from 20\% to 0\% fatal error rate (FER). The same trend for Confirm-and-Select with it reducing its FER from 12.5\% to 5\%. The authors, therefore, recommended ``Compare-and-Confirm'' as the overall best choice for comparison methods. Comparing this research to the work done by Kainda \textit{et al.}\cite{kainda2009usability}; this is consistent with their findings where they ranked ``Compare-and-Confirm'' as superior to that of ``Compare-and-Select'' in all regards.

Overall, the paper provides a sizeable insight into suitable methods of comparison, this is due to the cross over between fingerprint comparison and secure device pairing. This paper is limited in terms of the very short strings compared, the different overall research aim and the size of the number of participants used in the studies. In terms of overall recommendations, the results were consistent with that of alternative research with the exception of recommendations regarding ``Compare-and-Enter''. This, however, may be due to the differing use-cases of the comparison methods in the two respective studies.

@@

To provide a visual comparison the accuracy results of the papers have been provided in Table~\ref{tab:results} \& \ref{tab:times}. Each paper used a unique accuracy representation, and, therefore, have been translated into overall accuracy. Due to some of the differing characteristics of the papers ultimately affecting results, Table \ref{tab:attacker} has also be provided. This table is useful to compare the health of the studies and chosen sizes that may affect the accuracy and reliability of the results.

\begin{table}
    \makebox[\textwidth][c]{
        \input{tables/fingerprint_comparison.tex}
    }%
    \caption{Accuracy of correct comparison for the encoding schemes assessed}
    \label{tab:results}
\end{table}

\begin{table}
    \makebox[\textwidth][c]{
        \input{tables/fingerprint_times.tex}
    }%
    \caption{Timing results in seconds for the related schemes}
    \label{tab:times}
\end{table}

\begin{table}
    \makebox[\textwidth][c]{
        \input{tables/fingerprint_attacker_stren.tex}
    }%
    \caption{Paper attribute comparison}
    \label{tab:attacker}
\end{table}

In conclusion for this section, there has been extensive work in the investigation of the usability of textual and visual encoding schemes alongside methods of comparison. There are mixed opinions about visual representations, however, the majority defines them as easy to use but severely lacking in security. This can be seen in Table~\ref{tab:times} with graphical schemes having significantly lower comparison times in comparison to all alternatives. \\
Research on textual representations, however, is in agreement; natural language based encodings such as Words or Sentences provide some of the highest usability and security over the baseline performance of alphanumerical encodings. This again, can be seen from Table~\ref{tab:results} \& \ref{tab:times}, where consistently Word and Sentences has some of the highest accuracy and lowest comparisons across the various studies.\\
The literature also concurs on the use of Compare-and-Confirm as the best method of comparing fingerprints overall, with Compare-and-Select being highlighted for its poor security and usability.\\
The starkest limitations of the literature are the range of participant and encoding entropy, where at its worst only 22-bits of entropy were tested (See Table \ref{tab:attacker}) Another limitation is the scant amount of research solely investigating modes of comparison, where the literature only contains two papers with this aim. This is, therefore, an area that requires further research. A potential research avenue could be the analysis of comparison methods in unique scenarios, one example of this could be the idea of ``remote-vs-proximity'' proposed by M. Shirvanian \textit{et al.}\cite{shirvanian2017pitfalls}. \\
Even with these limitations, as a whole the literature on this topic has provided a relatively comprehensive and coherent view on the usability of textual and visual hash encoding schemes with relatively clear recommendations on methods of comparison and suitable encoding schemes.

### 2019-07-22 Thesis/pages/lit_review.tex
Changes; - Added inital files for Thesis write up - Ordered and restructured various documents - Moved old lit' review into the .archive

% \section{Introduction}
% The increasing use of public key cryptography by instant messaging and secure email means key fingerprint 
% verification is an ever more important task. One of the most significant risks to the security of the communication channel is a Man-in-the-middle (MiTM) attack. A successful MiTM attack can circumvent the encryption as it allows an attacker to read all the encrypted data. A countermeasure for this is the verification of each parties' fingerprint. \textbf{[...]}

% \textbf{TODO: } Finish introduction

\section{Literature Review}

Fingerprints are used to compare the similarity of two keys quickly. The comparison occurs between two digests of a secure one-way hash function. Historically these have been represented as a hexadecimal string whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card.
This process is known as the \textit{``authentication ceremony.''} \\
Prior research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}. This rules out the possibility of comparing complete digests. For example, SHA-1 is 40 hex digits (160-bit) and, therefore, difficult to effectively compare. Therefore, if human interaction is required; there is a need for schemes that work effectively with consideration to individual limitations.

@@

\subsection*{Definition of terms}
Throughout the paper, various terms are used to define elements of the authentication ceremony relevant to fingerprints verification. Explicit descriptions are, therefore, stated in this section. These are used to remove ambiguity and underlying associations readers may have for the words chosen.

\textbf{\textit{Encoding schemes}} - This is the physical method of encoding used to represent the fingerprint. For example, ``Hexadecimal'' or ``Words'' are a unique way to represent a fingerprint and thus, are encoding schemes.

\textbf{\textit{Method of comparison}} - This is how the user assesses the encoding scheme. The most common example and the one used as default is ``Compare-and-Confirm'' (CaC). CaC, as the name suggests, is the \textit{comparison} of two fingerprints on different devices or mediums that are then \textit{confirmed}. The following sections explain alternative methods of comparisons.

@@

\subsection*{Encoding scheme performance}
Results 
from the literature consistently show the effectiveness of language-based encodings such as Words or Sentences with accuracies ranging from 94\% \cite{dechand2016empirical}\cite{tan2017can}\cite{kainda2009usability}. In all cases, these were the best schemes from the sets assessed. The exception to this is the work performed by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63.00\%.
\\\\
Aside from textual representations were graphical schemes. Examples of schemes assessed were: Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Vash\footnote{https://github.com/thevash/vash}, OpenSSH visual host key and Unicorns\footnote{https://unicornify.pictures/}, among others. These schemes had mixed accuracy with ranges as large as 50\% - 94\% in work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study}. The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can} where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
\\
In terms of usability of graphical schemes, the literature concurred on their high usability. The comparison speed of these schemes were all among the quickest (See Table \ref{tab:times} for an overview of timings). Other work also indirectly concurred with graphical encodings having significantly quicker comparison times compared to non-graphical schemes \cite{dechand2016empirical}\cite{kainda2009usability}.
In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with literature only containing two papers. There is also no overlap in the schemes assessed with each paper reviewing a unique set. This is, therefore, a promising candidate for further research.

@@

Tables~\ref{tab:results} \& \ref{tab:times} contain the accuracy results of all papers assessed; this is to aid in visual comparison. Each paper used a different metric for measuring accuracy. Therefore, all results have been translated into ``overall accuracy.''

>>>>

\chapter{Literature Review}
\label{cha:LiteratureReview}

Fingerprints are used to compare the similarity of two keys quickly. The comparison occurs between two digests of a secure one-way hash function. Historically these have been represented as a hexadecimal string whereon verification fingerprints are compared between two substrates, for example, a monitor screen and a business card.
This process is known as the \textit{``authentication ceremony.''}

Prior research has shown that the average human can only hold around 7-digits worth of data in their working memory\cite{miller1956magical}. This rules out the possibility of comparing complete digests. For example, SHA-1 is 40 hex digits (160-bit) and, therefore, difficult to effectively compare. Therefore, if human interaction is required; there is a need for schemes that work effectively with consideration to individual limitations.

@@

\subsection*{Definition of terms}
Throughout the paper, various terms are used to define elements of the authentication ceremony relevant to fingerprints verification. Explicit descriptions are, therefore, stated in this section. These are used to remove ambiguity and underlying associations readers may have for the words chosen.
\\\\
\textbf{\textit{Encoding schemes}} - This is the physical method of encoding used to represent the fingerprint. For example, ``Hexadecimal'' or ``Words'' are a unique way to represent a fingerprint and thus, are encoding schemes.
\\\\
\textbf{\textit{Method of comparison}} - This is how the user assesses the encoding scheme. The most common example and the one used as default is ``Compare-and-Confirm'' (CaC). CaC, as the name suggests, is the \textit{comparison} of two fingerprints on different devices or mediums that are then \textit{confirmed}. The following sections explain alternative methods of comparisons.

@@

\subsection*{Encoding scheme performance}
Results 
from the literature consistently show the effectiveness of language-based encodings such as Words or Sentences with accuracies ranging from 94\% \cite{dechand2016empirical}\cite{tan2017can}\cite{kainda2009usability}. In all cases, these were the best schemes from the sets assessed. The exception to this is the work performed by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study} in 2009 with Words achieving an abnormal accuracy of 63.00\%.
\\\\
Aside from textual representations were graphical schemes. Examples of schemes assessed were: Random Art\cite{perrig1999hash}, Flag\cite{ellison2003public}, T-Flag\cite{lin2010spate}, Vash\footnote{https://github.com/thevash/vash}, OpenSSH visual host key and Unicorns\footnote{https://unicornify.pictures/}, among others. These schemes had mixed accuracy with ranges as large as 50\% - 94\% in work by \textbf{Hsiao, \textit{et al.}}\cite{hsiao2009study}. The only other paper assessing graphical representations was the work of \textbf{Tan \textit{et al.}}\cite{tan2017can} where they also achieved mixed results with accuracies ranging from 46\% to 90\%.
\\
\begin{table}[h!]
    \makebox[\textwidth][c]{
        \input{tables/fingerprint_times.tex}
    }%
    \caption{Timing results in seconds for the related schemes}
    \label{tab:times}
\end{table}
\\
In terms of usability of graphical schemes, the literature concurred on their high usability. The comparison speed of these schemes were all among the quickest (See Table \ref{tab:times} for an overview of timings). Other work also indirectly concurred with graphical encodings having significantly quicker comparison times compared to non-graphical schemes \cite{dechand2016empirical}\cite{kainda2009usability}.
In terms of research into the performance of graphical schemes, the literature does not contain an extensive review with literature only containing two papers. There is also no overlap in the schemes assessed with each paper reviewing a unique set. This is, therefore, a promising candidate for further research.

@@

\begin{table}[h!]
    \makebox[\textwidth][c]{
        \input{tables/fingerprint_comparison.tex}
    }%
    \caption{Accuracy of correct comparison for the encoding schemes assessed}
    \label{tab:results}
\end{table}

Tables \ref{tab:times} \& \ref{tab:results} contain the accuracy results of all papers assessed; this is to aid in visual comparison. Each paper used a different metric for measuring accuracy. Therefore, all results have been translated into ``overall accuracy.''

### 2019-07-22 Thesis/tables/fingerprint_attacker_stren.tex
Changes; - Added inital files for Thesis write up - Ordered and restructured various documents - Moved old lit' review into the .archive

\begin{tabular}{c|ccccc}
    \toprule
                        & Hsu-Chun\cite{hsiao2009study}      
                        & Kainda\cite{kainda2009usability}      
                        & Dechand\cite{dechand2016empirical}
                        & Tan\cite{tan2017can}      
                        & M. Shirvanian\cite{shirvanian2017pitfalls}
                        \\\hline
    Attacker Strength\footnote{Some attacker strengths are estimations due to the lack of quantification in some papers.}   
    & $\sim2^{28}$  & $\sim2^{40}$ & $2^{80}$ & $2^{60}$ & $\sim2^{242}$ \\
    Entropy Range       & 22-28 bits    & 20-40 bits   & 122 bits & 128 bits & 160-256 bits  \\
    No\degree  ~Participants     & 436           & 30           & 1047     & 661      & 25            \\
    \bottomrule
\end{tabular}

>>>>

\begin{tabular}{c|ccccc}
    \toprule
                        & Hsu-Chun\cite{hsiao2009study}      
                        & Kainda\cite{kainda2009usability}      
                        & Dechand\cite{dechand2016empirical}
                        & Tan\cite{tan2017can}      
                        & M. Shirvanian\cite{shirvanian2017pitfalls}
                        \\\hline
    Attacker Strength\footnote{Some attacker strengths are estimations due to the lack of quantification in some papers.}   
    & $\sim2^{28}$  & $\sim2^{40}$ & $2^{80}$ & $2^{60}$ & $\sim2^{242}$ \\
    Entropy Range       & 22-28 bits    & 20-40 bits   & 122 bits & 128 bits & 160-256 bits  \\
    No\degree  ~Participants     & 436           & 30           & 1001     & 661      & 25            \\
    \bottomrule
\end{tabular}
